\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-26 doc/sui14/relatedwork.tex
Added info about CV approaches

>>>>

\subsection{Markers and Vision Methods}
\achal{Not sure where to put this, feel free to move.}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on passive tags on devices, combined with computer vision methods for
detection. Unfortunately, these methods either impose significant constraints
on the camera used for detection, or require large, obtrusive tags, and
inevitably lack feedback from passive devices in the environment. \cite{Bokode},
for example, relies on visually imperceptible codes, but has significant
drawbacks: despite using a 12.1 megapixel DSLR camera, detections are no
longer robust past an angle of 20. Similarly, in our experiments, we found
that striking a balance between the size of the tag, the prices of the
device, and the computational cost of detection was unfeasible with current
cameras and algorithms.}

\ben{Reviewers suggest considering computer vision-based techniques with markers in the environment (such as QR codes, or Bokode [Mohan] which extends the working distance to a few meters for visual tags). We considered this direction and found several drawbacks, including computational complexity, low accuracy when targets are far, the absence of real-time environment feedback with passive tags, and aesthetic issues with QR codes. While we don't claim our choice of IR is optimal, it has important advantages -- it is low-cost, readily available and quite suitable for area selection. We can weaken our claim and add explanations of how disambiguation techniques might generalize to other methods of implementing target identification.}

\achal{Read and discussed the Bokode paper and CV in general. Unsure about what
to do regarding "weakening our claim."}
